News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-05 rupnik2015.tex
intro

As input we consider a high volume of articles in different languages. By using a language detector the stream is split into separate monolingual streams. Within each monolingual stream, an online clustering approach is employed, where tracked clusters correspond to our definition of events - this is based on the Event Registry system \shortcite{Leban2014W,Leban2014I}. Our main goal in this paper is to connect such clusters (representations of events) across languages, that is, to detect that a set of articles in language $A$ reports on the same event as a set of articles in language $B$.

Our approach to linking clusters across languages combines two ingredients: a cross-lingual document similarity measure, which can be interpreted as a language independent topic model, and semantic annotation of documents, which enables an alternative way to comparing documents.

@@

Based on the similarity function we propose a novel algorithm for linking events/clusters across languages. The approach is based on learning a classification model from labelled data based on several sets of features. In addition to these features, cross-lingual similarity is also used to quickly identify a small list of potential linking candidates for each cluster.
This greatly increases the scalability of the system.

>>>>

 We consider a high volume of articles in different languages. By using a language detector, the stream is split into separate monolingual streams. Within each monolingual stream, an online clustering approach is employed, where tracked clusters correspond to our definition of events - this is based on the Event Registry system \shortcite{Leban2014W,Leban2014I}. Our main goal in this paper is to connect such clusters (representations of events) across languages, that is, to detect that a set of articles in language $A$ reports on the same event as a set of articles in language $B$.

Our approach to linking clusters across languages combines two ingredients: a cross-lingual document similarity measure, which can be interpreted as a language independent topic model, and semantic annotation of documents, which enables an alternative way to comparing documents. Since this work represents a complicated pipeline, we concentrate on these two specific elements. Overall, the approach should be considered from a systems' perspective (considering the system as a whole) rather than considering these problems in isolation.

@@

Based on the similarity function, we propose a novel algorithm for linking events/clusters across languages. The approach is based on learning a classification model from labelled data based on several sets of features. In addition to these features, cross-lingual similarity is also used to quickly identify a small list of potential linking candidates for each cluster.
This greatly increases the scalability of the system.
